End-User Software Customization by Direct Manipulation of Tabular Data

### 2020-08-15 paper.tex
final tweaks

  We illustrate the approach with Wildcard, a browser extension that
  implements data-driven customization on the web using web scraping.
  Through concrete examples, we show that this paradigm can support
  useful extensions to many real websites, and we share reflections from
  our experiences using Wildcard.

  Finally, we share our broader vision for a future where end users have
  greater access to the data in their applications, and better tools for
  taking advantage of that data in the context of everyday software
  usage.
\end{abstract}

@@

To explore this idea in a real context, we have developed a browser
extension called Wildcard that uses web scraping techniques to implement
data-driven customization for existing Web applications. We introduce
the tool with an example customization of Hacker News in
Section~\ref{sec:example}, and then describe the implementation in
{[}Section~\ref{sec:architecture}. In Section~\ref{sec:reflections}, we
present evidence that Wildcard can produce useful customizations, by
sharing reflections from customizing 11 different websites in ways that
met our own personal needs.

@@

DOM scraping adapters enable Wildcard to interface with an existing
website UI. A DOM scraping adapter fulfills the standard web scraping
task of extracting a table of data from the DOM, but it must also handle
the reverse direction: manipulating the DOM to reflect edits to the
table.

Currently, we require DOM scraping adapters to be programmed manually
for each website using Javascript code. It might seem that this
prohibits non-programmer users from using the system, but we solve this
problem via a shared repository of adapters. Once an adapter is
programmed for a website, it is added to a shared code repository,
enabling any end user to perform customizations on that website.

There are other ways a DOM scraping adapter could be produced which
would reduce this dependence on programmers: an end user could specify
the scraping logic via demonstration, or the desired data table could be
automatically inferred from the page. While we are interested in these
techniques and discuss them later in Section~\ref{sec:visions}, we
believe that a shared repository of manually programmed adapters is a
pragmatic starting point; given that many users visit the same popular
websites,a critical mass of adapters could serve the needs of many
users.

To ease the burden on programmers of creating these adapters, we have
created a framework makes the process feel more like writing
unidirectional scraping code than performing a complex bidirectional
synchronization. The key idea is this: programmers return pointers to
DOM elements representing table rows and table cells; Wildcard extracts
data from these DOM elements, but it also uses the pointers to
synchronize table edits back into the page. For example, when the user
sorts the table, the DOM elements representing the table rows are moved
around in the DOM to reflect the new sorted order.

>>>>

  We illustrate the approach with Wildcard, a browser extension that
  implements data-driven customization on the web using web scraping.
  Through concrete examples, we show that this paradigm can support
  useful extensions to many real websites, and we share reflections from
  our experiences using the tool.

  Finally, we share our broader vision for data-driven customization: a
  future where end users have greater access to the data inside their
  applications, and better tools for flexibly making use of that data in
  the context of everyday software usage.
\end{abstract}

@@

To explore this idea in a real context, we have developed a browser
extension called Wildcard that uses web scraping techniques to implement
data-driven customization for existing Web applications. We introduce
the tool with an example customization of Hacker News in
Section~\ref{sec:example}, and then describe the implementation in
Section~\ref{sec:architecture}. In Section~\ref{sec:reflections}, we
present evidence that Wildcard can produce useful customizations, by
sharing reflections from customizing 11 different websites in ways that
met our own personal needs.

@@

DOM scraping adapters enable Wildcard to interface with an existing
website UI. A DOM scraping adapter fulfills the standard web scraping
task of extracting a table of data from the DOM, but it also acts in the
reverse direction: manipulating the DOM to reflect edits to the table.

In Wildcard, DOM scraping adapters are programmed manually for each
website using Javascript code. It might seem that this prohibits
non-programmer users from using the system at all, but we solve this
problem via a shared repository of adapters. Once an adapter is
programmed for a website, it is added to the shared repository, enabling
any end user to perform customizations on that website.

In the future, other strategies for producing DOM scraping adapters
could reduce this dependence on programmers: an end user could specify
the scraping logic via demonstration, or the desired data table could be
automatically inferred from the page. While we are interested in these
techniques and discuss them in Section~\ref{sec:visions}, we believe
that a shared repository of manually programmed adapters is a pragmatic
starting point; given that many users visit the same popular websites,a
critical mass of adapters could serve the needs of many users.

To make it easier to create these adapters, Wildcard provides a
framework that makes the process feel more like writing unidirectional
scraping code than performing a complex bidirectional synchronization.
The key idea is this: programmers return pointers to DOM elements
representing table rows and table cells; Wildcard extracts data from
these DOM elements, but it also uses the pointers to synchronize table
edits back into the page. For example, when the user sorts the table,
the DOM elements representing the table rows are moved around in the DOM
to reflect the new sorted order.
